---
title: "rGenomeTracksData"
author: "Omar Elashkar"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rGenomeTracksData}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

rGenomeTracksData is a collection of sample genomic and epigenomic data for demonstrating rGenomeTracks package.

## Data Source 
This data is provided by [pyGenomeTracks](https://github.com/deeptools/pyGenomeTracks) project.

## File types 

| Name                                       | Type                          |
|--------------------------------------------|-------------------------------|
| bigwig2_X_2.5e6_3.5e6.bw                   | bigwig                        |
| dm3_genes.bed.gz"                          | bed12                         |
| dm3_genes.bed4.gz"                         | bed4                          |
| dm3_genes.bed6.gz"                         | bed6                          |
| dm3_subset_BDGP5.78.gtf.gz"                | gtf                           |
| epilog.qcat.bgz"                           | qcat                          |
| GSM3182416_E12DHL_WT_Hoxd11vp.bedgraph.gz" | bedGraph                      |
| HoxD_cluster_regulatory_regions_mm10.bed"  | bed                           |
| Li_et_al_2015.cool                         | HDF5 compressed sparse (cool) |
| Li_et_al_2015.h5                           | HDF5                          |
| links2.links                               | bed links                     |
| tad_classification.bed                     | bed                           |
| test.arcs                                  | bed links                     |
| test2.narrowPeak                           | narrowPeak                    |

## Installation and loading of libraries
```{r install, eval = FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("ObMiTi")
```


```{r setup}
# loading required libraries
library(rGenomeTracksData)
library(AnnotationHub)
```

## Query AnnotationHub
```{r}
ah <- AnnotationHub()
query(ah, "rGenomeTracksData")
```

## Fetch Data 

After saving the query object, you can access the file you want like that: 
```{r}
# locate the file you want for loading from the track
bigwig_file <-  ah[["AH95891"]]
```
The object is a path to the local directory to the downloaded file. 

## Session Info 

```{r session_info}
sessionInfo()
```
