---
title: "rGenomeTracksData"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rGenomeTracks}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

rGenomeTracksData is a collection of sample genomic and epigenomic data for demonstrating rGenomeTracks package.

## Data Source 
This data is provided by [pyGenomeTracks](https://github.com/deeptools/pyGenomeTracks) project.

## File types 

| Name                                       | Type                          |
|--------------------------------------------|-------------------------------|
| bigwig2_X_2.5e6_3.5e6.bw                   | bigwig                        |
| dm3_genes.bed.gz"                          | bed12                         |
| dm3_genes.bed4.gz"                         | bed4                          |
| dm3_genes.bed6.gz"                         | bed6                          |
| dm3_subset_BDGP5.78.gtf.gz"                | gtf                           |
| epilog.qcat.bgz"                           | qcat                          |
| GSM3182416_E12DHL_WT_Hoxd11vp.bedgraph.gz" | bedGraph                      |
| HoxD_cluster_regulatory_regions_mm10.bed"  | bed                           |
| Li_et_al_2015.cool                         | HDF5 compressed sparse (cool) |
| Li_et_al_2015.h5                           | HDF5                          |
| links2.links                               | bed links                     |
| tad_classification.bed                     | bed                           |
| test.arcs                                  | bed links                     |
| test2.narrowPeak                           | narrowPeak                    |

```{r setup}
library(rGenomeTracksData)
```


```{r}
# List all package
list.files(system.file("extdata", package = "rGenomeTracksData"))

# locate the file you want for loading from the track

bigwig <- system.file("extdata", package = "rGenomeTracksData", file = "bigwig2_X_2.5e6_3.5e6.bw")
```

## Session Info 

```{r}
sessionInfo()
```
